An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-02-27 journal/poly-embed.tex
Added proof of Theorem 3 as well.

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property. \jessie{type check??}
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	Let $\L$ be a polyhedral loss, and $\Gamma$ by the unique property it elicits.
	By Theorem~\ref{thm:poly-embeds-discrete}, we know there is a discrete loss $\ell$ embedded by $L$.
	Take $\gamma$ to be the finite property elicited by $\ell$.
	\jessie{TODO After clarifying with Raf and Bo}
\end{proof}
\begin{proof}[Original]
	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

@@

>>>>

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property. \jessie{type check??}
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}[Original]
	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.  Rinse and repeat for vertices of the expected loss on all possible (finite) supports.  As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?  Unclear on that gap.}
	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

@@

\begin{definition}\label{def:indirectly-elicits}
	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
\end{definition}
Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.

\begin{theorem}[Theorem 3, but type checked]
	A polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a loss $\ell$ eliciting property $\gamma'$ which refines $\gamma$.
\end{theorem}
\begin{proof}
	$\Rightarrow$: 
	Since $L$ is polyhedral, we know it embeds some discrete loss $\ell$ by Theorem~\ref{thm:poly-embeds-discrete}.
	Call $\gamma := \prop{\ell}$, since $L$ embeds $\ell$, we have $L$ indirectly eliciting $\gamma$.
	Moreover, $\gamma$ trivially refines itself.

	$\Leftarrow$:
	This direction is a corollary of Proposition~\ref{prop:calibrated-link-refinement}.

\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\jessie{This is new from the NeurIPS submission.}
\begin{proposition}\label{prop:calibrated-link-refinement}
	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proposition}
\begin{proof}
	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
